Importance of depth refugia for reef resilience and intervention on the Great Barrier Reef under future climate change

### 2025-09-25 paper/paper_draft.qmd
Format rf tables for rendering with labels
@ConnectedSystems for some reason the table got removed by my earlier commit. Had to copy it over again.

A 3-fold cross-validation was also conducted, arriving at a similar 59% accuracy rate.
Furthermore, F1 performance scores for Low, Medium, and High clusters were determined to be
0.70, 0.41 and 0.63 respectively, with precision of 0.77, 0.47 and 0.64 when evaluated with
the test set (consisting of 4394 samples). Lower performance with the Medium cluster
reflects the inherent difficulty of classifying transitional states in natural systems. The
consistent level of accuracy across test and cross-validation demonstrates the generalised
performance of the RF classifier, while not accurate, was deemed sufficiently informative
for the purpose of assessing the influence of reef characteristics.

@@

>>>>

A 3-fold cross-validation was also conducted, arriving at a similar 59% accuracy rate.
Furthermore, F1 performance scores for Low, Medium, and High clusters were determined to be
0.70, 0.43 and 0.64 respectively, with precision of 0.62, 0.51 and 0.66 when evaluated with
the test set (consisting of 4394 samples) [@stbl-confusion-matrix;
@stbl-rf-cluster-performance]. Lower performance with the Medium cluster reflects the
inherent difficulty of classifying transitional states in natural systems. The consistent
level of accuracy across test and cross-validation demonstrates the generalised performance
of the RF classifier, while not accurate, was deemed sufficiently informative for the
purpose of assessing the influence of reef characteristics.

@@

#### Random Forest Performance

::: {#stbl-confusion-matrix}
|               |         | **Ground Truth** |          |
|---------------|---------|------------------|----------|
| **Predicted** | **Low** | **Medium**       | **High** |
| **Low**       | 1371    | 682              | 151      |
| **Medium**    | 247     | 603              | 340      |
| **High**      | 97      | 302              | 787      |

Confusion matrix for the Random Forest classifier used to assess partial dependence.
Diagonals indicate correctly classified time series clusters. Columns are the "true" cluster
memberships and indicate the samples that were correctly or incorrectly classified as
Low/Medium/High. For example, the first column shows the number of samples correctly
classified into the Low cluster, and the number of Low samples incorrectly classified as
being in either the Medium or High coral cover clusters. There were 4580 samples used for
testing.
:::

::: {#stbl-rf-cluster-performance}
|                  | **Low** | **Medium** | **High** |
|------------------|---------|------------|----------|
| **Test samples** | 1715    | 1587       | 1278     |
| **Precision**    | 0.622   | 0.507      | 0.664    |
| **Recall**       | 0.799   | 0.38       | 0.616    |
| **F1**           | 0.7     | 0.434      | 0.639    |

Performance metrics for the Random Forest classifier for each of the time series clusters.
:::
